Finiteness in Cubical Type Theory

### 2020-07-03 sections/search.tex
finished countdown section

The proof that this type is finite mirrors its definition closely:
\begin{agdalisting}
  \ExecuteMetaData[agda/Countdown.tex]{expr-finite}
\end{agdalisting}
\subsection{Filtering to Correct Expressions}
We now have a way to construct, formally, every expression we can generate from
a given list of numbers.
This is incomplete in two ways, however.
Firstly, some expressions are invalid: we should not, for instance, be able to
divide two numbers which do not divide evenly.
Secondly, we are only interested in those expressions which actually represent
solutions: those which evaluate to the target, in other words.
We can write a function which tells us if both of these things hold for a given
expression like so:
\begin{multicols}{2}
  \begin{agdalisting}
    \ExecuteMetaData[agda/Countdown.tex]{eval}
  \end{agdalisting} \columnbreak
  \begin{agdalisting}
    \ExecuteMetaData[agda/Countdown.tex]{app-op}
  \end{agdalisting}
\end{multicols}
\section{Automating Proofs}

>>>>

The proof that this type is finite mirrors its definition closely:
\begin{agdalisting}
  \ExecuteMetaData[agda/Countdown.tex]{expr-finite}
\end{agdalisting}
\subsection{Filtering to Correct Expressions}
We now have a way to construct, formally, every expression we can generate from
a given list of numbers.
This is incomplete in two ways, however.
Firstly, some expressions are invalid: we should not, for instance, be able to
divide two numbers which do not divide evenly.
Secondly, we are only interested in those expressions which actually represent
solutions: those which evaluate to the target, in other words.
We can write a function which tells us if both of these things hold for a given
expression like so:
\begin{multicols}{2}
  \begin{agdalisting}
    \ExecuteMetaData[agda/Countdown.tex]{eval}
  \end{agdalisting} \columnbreak
  \begin{agdalisting}
    \ExecuteMetaData[agda/Countdown.tex]{app-op}
  \end{agdalisting}
\end{multicols}

With this all together, we can finally write down the type of all solutions to a
given countdown problem.
\begin{agdalisting}
  \ExecuteMetaData[agda/Countdown.tex]{solution-type}
\end{agdalisting}
And, because the predicate here is decidable and a mere proposition, we can
prove that there are finitely many solutions:
\begin{agdalisting}
  \ExecuteMetaData[agda/Countdown.tex]{finite-solution}
\end{agdalisting}
And we can apply this to a particular problem like so:
\begin{agdalisting}
  \ExecuteMetaData[agda/Countdown.tex]{example-solution}
\end{agdalisting}

\section{Automating Proofs}
